---
title: "RICT Northern Ireland ALL Indices Version 1"
output: html_document
Author: Dr Maybin K. Muyeba
---

# This Script is the Northern Ireland versuion of the RICT model to predict various indices
# All data validation and transformation (conversion) are to be done in this script using functions predefined in HelperFunctionsNI_v1.R ( now renamed HelperFunctionsv1.and 
# PredictionfunctionsNI_v1 

```{r}
# 
#  This section reads in Environmental Base data from Biosys i.e. containing columns "SITE","Year","NGR", "Easting","Northing", .., "CONDUCTIVITY"
#  Converts some of the raw input, and converts Lat/Long into National Grid Reference
#
 
require(readxl) # requires tidyverse
require(rnrfa) # National River Flow Architecture 

library(dplyr)
library(magrittr)
library(sp)
library(sf)
library(data.table)

path <-  "C:/DEFRA/Phase2/RICT-NI-SingleYearSummerOnly_RSTUDIO_codes"
path_functions <- "C:/DEFRA/Phase2/RICT/supportfunctions"
path_datafiles <- "C:/DEFRA/Phase2/RICT/datafiles"


#source('C:/Users/Maybin/Documents/Rict/codes_JimKing/MeanAirTempAirTempRangeASFunction.R')
source(paste0(path_functions,'/Helperfunctionsv1.R'))
source(paste0(path_functions, '/PredictionfunctionsV2.R')) # PredictionfunctionsNI_V1.R'))

model <- c("RIVPACS IV NI")

# Set up dataframe for error messages, schema = "siteID", "column/feature", "msg"" 

# RUN the CLEAN National classification DATA
#raw.input.data <- readCSVFile(paste0(path_datafiles, "/NI _12SitesTestEnvInputData_Ralph.csv")) ##NI_TestData_Ralphv1.csv"))
raw.input.data  <- readCSVFile("C:/DEFRA/Phase2/RICT-NI-SingleYearSummerOnly_RSTUDIO_codes/datafiles/NI_TestData_Ralphv1.csv")

#Rename the column 1 from ?..SITE to "SITE"
colnames(raw.input.data)[1]  <- c("SITE") # change AZURE
raw.input.data$SITE <- as.character(raw.input.data$SITE) # change AZURE

#raw.input.data$SITE     <- as.character(raw.input.data$SITE)
# This part not necessary for RStudio, but for Machine Learning Studio
# check for length <5, add a "0" to get proper Easting/Northing 5 digit codes


raw.input.data$Easting  <- getCorrectCodes(raw.input.data$Easting)   # Change AZURE
raw.input.data$Northing <- getCorrectCodes(raw.input.data$Northing)  # Change AZURE

# Change all column names to uppercase
names(raw.input.data) <- toupper(names(raw.input.data)) # change AZURE
# Check if theres another column called "Waterbody", DROP IT

# Get all the bioligical data, including WaterBody, YEAR, CHANGE AZURE !!!TODAY

# new fread
namesBiological <-    c(colnames(raw.input.data)[1], colnames(raw.input.data)[2],colnames(raw.input.data)[3],"SPR_SEASON_ID", "SPR_TL2_WHPT_ASPT (ABW,DISTFAM)","SPR_TL2_WHPT_NTAXA (ABW,DISTFAM)", "SPR_NTAXA_BIAS", "SUM_SEASON_ID", "SUM_TL2_WHPT_ASPT (ABW,DISTFAM)","SUM_TL2_WHPT_NTAXA (ABW,DISTFAM)", "SUM_NTAXA_BIAS", "AUT_SEASON_ID", "AUT_TL2_WHPT_ASPT (ABW,DISTFAM)","AUT_TL2_WHPT_NTAXA (ABW,DISTFAM)","AUT_NTAXA_BIAS")
 
biologicalData <- raw.input.data[,..namesBiological, with = FALSE] # 
# Add failed sites; raw.input.data[raw.input.data$SITE==this_failing$SITE,]

# Choose the seasons to run 
#SEASONS_TO_RUN <- c(raw.input.data$SUM_SEASON_ID[1]) # change AZURE to SUMMER
SEASONS_TO_RUN <- c(raw.input.data$SPR_SEASON_ID[1], raw.input.data$SUM_SEASON_ID[1], raw.input.data$AUT_SEASON_ID[1]) # change AZURE

```


```{r}
raw.input.data <- validateEnvData (raw.input.data)

```

# Data validation
# 1. MEAN_WIDTH, lower_bound=1, upper_bound=37

```{r}
valid_mean_width <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
  valid_mean_width <- rbind(valid_mean_width,getValidEnvInput(raw.input.data$MEAN_WIDTH[i], 1, 37, "MEAN_WIDTH"))
}
# Change column names to suit env variable name, and cbind to original dataset
colnames (valid_mean_width) <- paste0("mn_width_",noquote(colnames(valid_mean_width)))
raw.input.data <- cbind(raw.input.data, valid_mean_width)

```

# Data validation
# 2. MEAN_DEPTH, lower_bound=1.7, upper_bound=300  

```{r}
valid_mean_depth <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
  valid_mean_depth <- rbind(valid_mean_depth,getValidEnvInput(raw.input.data$MEAN_DEPTH [i], 1.7, 300, "MEAN_DEPTH"))
}
colnames (valid_mean_depth) <- paste0("mn_depth_",noquote(colnames(valid_mean_depth)))
raw.input.data <- cbind(raw.input.data, valid_mean_depth)

```

# Data validation
# 3. SLOPE, lower_bound=0.1, upper_bound=50
```{r}

valid_slope <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
  valid_slope <- rbind(valid_slope,getValidEnvInput(raw.input.data$SLOPE [i], 0.1, 50, "SLOPE"))
}
colnames (valid_slope) <- paste0("vld_slope_",noquote(colnames(valid_slope))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_slope)
```

# Data validation
# 4. DIST_FROM_SOURCE, lower_bound=2.2, upper_bound=75,  

```{r}
valid_dist_src <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
  valid_dist_src <- rbind(valid_dist_src,getValidEnvInput(raw.input.data$DIST_FROM_SOURCE [i], 2.2, 75, "DIST_FROM_SOURCE"))
}
colnames (valid_dist_src) <- paste0("vld_dist_src_",noquote(colnames(valid_dist_src))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_dist_src)

```

# Data validation
# 5. ALTITUDE, has two sets of bounds, lower_bound=3, upper_bound=180, lower_low_bound=0, upper_up_bound = 1345
[0,1345] are hard coded, could be parameterised QED
```{r}

valid_altitude <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
  #valid_altitude <- rbind(valid_altitude,getAltitude(raw.input.data$ALTITUDE [i], 3, 180))
  valid_altitude   <- rbind(valid_altitude,getEnvVariableTwoBounds(raw.input.data$ALTITUDE [i], 3, 180, 0, 1345, "ALTITUDE"))
}

colnames (valid_altitude) <- paste0("vld_alt_src_",noquote(colnames(valid_altitude))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_altitude)

```

# Data validation
# 6. ALKALINITY, has bounds, lower_bound=2.5, upper_bound=366
# getLogAlkalinity <- function (hardness, calcium, conduct, alkal, lower_b, upper_b)

```{r}

valid_alkalinity <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
  valid_alkalinity <- rbind(valid_alkalinity,getLogAlkalinity(raw.input.data$HARDNESS[i], raw.input.data$CALCIUM[i], raw.input.data$CONDUCTIVITY[i],raw.input.data$ALKALINITY[i], 2.5, 366))
}
#Above loop same as # thiscopy <- as.data.frame(with(raw.input.data, mapply(getLogAlkalinity, HARDNESS, CALCIUM, CONDUCTIVITY, ALKALINITY, 1.2, 366)))
# thiscopy$V1$msg=="Succ"
colnames (valid_alkalinity) <- paste0("vld_alkal_",noquote(colnames(valid_alkalinity))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_alkalinity)

```
# Data validation
# 7. Validate SUBSTRATUM for sum of values "TOTSUB" in interval [97,103] exclussive,and MSUBSTR in interval [-8, 8]. Write to a file if errors found
# Remove the site or records with such errors, and continue the prediction

# getSubstrate <- function(bould_cob, pebbles_gr, snd, silt_cl, lower_b, upper_b) 

```{r}
valid_substrate <- data.frame(log=as.numeric(), msg=as.character()) # Note that we don't use log for calculation of substrate
for(i in 1:nrow(raw.input.data)){
  valid_substrate <- rbind(valid_substrate,getSubstrate (raw.input.data$BOULDER_COBBLES[i], raw.input.data$PEBBLES_GRAVEL[i], raw.input.data$SAND[i], raw.input.data$SILT_CLAY[i], 0, 100))
}
colnames (valid_substrate) <- paste0("vld_substr_",noquote(colnames(valid_substrate))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_substrate)

```
 
# Data validation and conversion
# 8. Discharge category, bounds [1, 10]. Discharge calculated from velocity if not provided using width, depth

```{r}
valid_discharge <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
    #valid_discharge <- rbind(valid_discharge, getLogDischarge_NI(raw.input.data$MEAN_DEPTH[i], raw.input.data$MEAN_WIDTH[i], raw.input.data$DISCHARGE [i], raw.input.data$VELOCITY[i],1, 10))
     valid_discharge <- rbind(valid_discharge, getLogDischarge(raw.input.data$MEAN_DEPTH[i], raw.input.data$MEAN_WIDTH[i], raw.input.data$DISCHARGE [i], raw.input.data$VELOCITY[i],0, 10, 1,8))
}
colnames (valid_discharge) <- paste0("disch_",noquote(colnames(valid_discharge)))
raw.input.data <- cbind(raw.input.data, valid_discharge)
 
```

# Data validation and conversion
# 9. Calculation of Lat/Long

```{r}
# Calculation of Lat/Long using BNG (British National Grids)
# Use function getLatLong_NI()
  
#### Calculate Latitude #####
lat.long <- getLatLong_NI (raw.input.data$EASTING,raw.input.data$NORTHING)

raw.input.data$LATITUDE  <- lat.long$Latitude
raw.input.data$LONGITUDE <- lat.long$Longitude

# print(c("lat.long = ",lat.long))
valid_longitude <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
   valid_longitude <- rbind(valid_longitude,getLongitude(raw.input.data$LONGITUDE [i], -8.1, -5.7)) 
}
colnames (valid_longitude) <- paste0("vld_long_src_",noquote(colnames(valid_longitude))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_longitude)

# print(c("lat.long = ",lat.long))
valid_latitude <- data.frame(log=as.numeric(), msg=as.character())
for(i in 1:nrow(raw.input.data)){
   valid_latitude <- rbind(valid_latitude,getLatitude(raw.input.data$LATITUDE [i], 54, 55.2)) 
}
colnames (valid_latitude) <- paste0("vld_lat_src_",noquote(colnames(valid_latitude))) # vld = valid
raw.input.data <- cbind(raw.input.data, valid_latitude)
# Use Ralphs long/LAT

```

# Data validation and conversion 
# Data validation and conversion SKIP this , include all warnings in the output dataset
# 12. Write to file all Warnings and Failrures: SITE, MSG, iterate through the list of all variables with vld

```{r}
# Deal with altitude warnings
# Select columns only that end with "_msg"
msg_columns <- names(select(raw.input.data, ends_with("_msg")))
 
```


```{r}
# Deal with all warnings, save them in a file,  
# Same as above, but using pipes, and using all the variables
#msg_columns <- names(select(raw.input.data, ends_with("_msg")))
this_warning <- raw.input.data %>%    
         filter(substr(vld_alt_src_msg,1,5)=="Warn:"    | substr(mn_width_msg,1,5)=="Warn:" 
                | substr(mn_depth_msg,1,5)=="Warn:"     | substr(vld_alkal_msg,1,5)=="Warn:"
                | substr(disch_msg,1,5)=="Warn:"        | substr(vld_substr_msg,1,5)=="Warn:"
                | substr(vld_dist_src_msg,1,5)=="Warn:" | substr(vld_slope_msg,1,5)=="Warn:" )%>%
         select("SITE","YEAR",msg_columns) # Select some columns
write.csv(this_warning, file = paste0(path,"/NI_AllWarnings_file_data.csv"))
# which rows are these 
raw.input.data[which(this_warning[1,1] %in% raw.input.data[,c("SITE")]),]

```

# Data validation and conversion,  
# 13.1 Remove those instances where prediction is not runnable e.g. Fail warnings, and put these in one file with warnings

```{r}
# Deal with all failings, save them in a file
this_failing <- raw.input.data %>%    
         filter(substr(vld_alt_src_msg,1,5)=="Fail:"    | substr(mn_width_msg,1,5)=="Fail:" 
                | substr(mn_depth_msg,1,5)=="Fail:"     | substr(vld_alkal_msg,1,5)=="Fail:"
                | substr(disch_msg,1,5)=="Fail:"        | substr(vld_substr_msg,1,5)=="Fail:"
                | substr(vld_dist_src_msg,1,5)=="Fail:" | substr(vld_slope_msg,1,5)=="Fail:" )%>%
         select("SITE","YEAR",msg_columns) # Select some columns

AllFails_Warings <- rbind(this_warning, this_failing)           
write.csv(AllFails_Warings, file = paste0(path,"/Results/NI_Failings_file_data.csv"))
```

# Data validation and conversion,  
# 13.2 subset the instances to run in prediction by removing "this_failing", use anti-join i.e."Return all rows from x where there are not matching values in y, keeping just columns from x. This is a filtering join"

```{r}
final.predictors <- anti_join(raw.input.data, this_failing)
# or use below
# final.predictors1 <- raw.input.data[is.na(match(raw.input.data$SITE, this_failing$SITE)), ]

# final.predictors <- final.predictors[order(final.predictors$SITE),] # We dont need this in RStudio, but in ML AZURE, we need the sorting 

```


# Generate data for classification 
 
```{r}
# Final Data for classification e.g. Linear discriminant Analysis (LDA) classifier/predictor

final.predictors <- data.frame(
  SITE                     <-  final.predictors$SITE,
  LATITUDE                 <-  final.predictors$LATITUDE,
  LONGITUDE                <-  final.predictors$LONGITUDE,
  LOG.ALTITUDE             <-  final.predictors$vld_alt_src_log, # missin null
  LOG.DISTANCE.FROM.SOURCE <-  final.predictors$vld_dist_src_log,
  LOG.WIDTH                <-  final.predictors$mn_width_log,
  LOG.DEPTH                <-  final.predictors$mn_depth_log,
  MEAN.SUBSTRATUM          <-  final.predictors$vld_substr_log,
  DISCHARGE.CATEGORY       <-  final.predictors$DISCHARGE,    #raw.input.data$disch_log,
  ALKALINITY               <-  final.predictors$ALKALINITY,
  LOG.ALKALINITY           <-  final.predictors$vld_alkal_log,
  LOG.SLOPE                <-  final.predictors$vld_slope_log
  #MEAN.AIR.TEMP            <-  final.predictors$TMEAN,
  #AIR.TEMP.RANGE           <-  final.predictors$TRANGE
)

colnames(final.predictors) <- c("SITE","LATITUDE","LONGITUDE","LOG.ALTITUDE","LOG.DISTANCE.FROM.SOURCE","LOG.WIDTH","LOG.DEPTH","MEAN.SUBSTRATUM","DISCHARGE.CATEGORY","ALKALINITY","LOG.ALKALINITY", "LOG.SLOPE")


```
 
#  Prediction Settings
## 1. Enter 
```{r}
 
DFMean_NI <- read.delim(paste0(path,"/dataFiles/DFMEAN_NI_RALPH.DAT"), header = FALSE, sep="", as.is=TRUE)
DFCoeff_NI <- read.delim(paste0(path,"/datafiles/DFCOEFF_NI.DAT"), header = FALSE, sep="", as.is=TRUE)

```

#   Prediction Settings
#2. Find the DFScores of each row using one line of coefficients DFCoeff_gb685[1,-1] # removes the first column

```{r}
# NRefg = number of reference sites in end group g , for GB = 43, for NI = 11
#NRefg <- 685
# Get this from the EndGrp_AssessScores.csv file
NRefg_groups<- read.csv(paste0(path,"/dataFiles/EndGrp_AssessScoresNI.csv"))
# Remove first column, add up the rows
NRefg_all <- rowSums(NRefg_groups[,-1])
 
#DFScore_g <- DFCoef1 * Env1 + ... + DFCoefn * Envn ; remove "SITE" col=1 from final.predictors, and  remove col=1 from DFCoeff_gb685
# START HERE - Mutiply WRONG for DFScores *****
DFScores <- getDFScores(final.predictors, DFCoeff_NI)

# Calculate the Mahanalobis disance of point x from site g for all referene sites, and give column names
MahDist_g <- getMahDist(DFScores , DFMean_NI)
MahDistNames <- c("p1","p2","p3","p4","p5","p6","p7","p8","p9","p10","p11")

#Substitute 'p' for 'Mah'
MahDistNames <- gsub("p","Mah",MahDistNames)
colnames(MahDist_g) <- MahDistNames

# Calculate the minimum Mahanalobis disance of point x from site g
MahDist_min <- getMahDist_min(DFScores , DFMean_NI)
#Calculate the probability distribution
PDist_g <- PDist (NRefg_all, MahDist_g)

#Main dataframe needed:: Calculate probabilities of sites belonging to the endgroups, prob_g, l,as last column 44 contains the total "PGdistTot
PDistTot <- PDistTotal(PDist_g) ## ALL probabilities p1..pn,  rowsums() add to 1, except when last row which is "total" needs removing
# i.e. rowSums(PDistTot[,-ncol(PDistTot)])=1

# Rename the columns to probabilities p1,p2,...,p43
colnames(PDistTot) <- c("p1","p2","p3","p4","p5","p6","p7","p8","p9","p10","p11","Total" )

#Combine with final data to see probabilities of each site wrt endGroups (43 of them, so 43 probabilites), per row
final.predictors_try1 <- cbind(final.predictors, PDistTot[,-ncol(PDistTot)]) # sum(final.predictors_try[1,-c(1:14)]) should give 1

```

#3.Use chisquare to find suitability codes. Start for Britain GB
# 1 = GB 21.02606 24.05393 26.21696 32.90923 
# 2 = NI 18.30700 21.16080 23.20930 29.58830
# Could use a file for these chisquare values

```{r}
#Enter these as csv file
chiSquare_vals <- data.frame(CQ1=c(21.02606, 18.30700), CQ2=c(24.05393,21.16080), CQ3=c(26.21696,23.20930), CQ4=c(32.90923,29.58830))
suitCodes <- getSuitabilityCode(MahDist_min, chiSquare_vals)
# add suitab ility codes to the final data, using cbind 
final.predictors_try2 <- cbind(final.predictors_try1, suitCodes)
#Write to csv

```

# Find max class group belongs to by getting the column name: use
# colnames(final.predictors_try[,15:57])[apply(final.predictors_try[,15:57], 1, which.max)]

```{r}
#Basically search for the start of probability columns - 13:23 using an abstraction of or grep, or match or ends_with in dplyr

BelongsTo_endGrp <- colnames(final.predictors_try2[,13:23])[apply(final.predictors_try2[,13:23], 1, which.max)] # # This sometimes returns a list,
# use unlist below to repair this
# BelongsTo_endGrp <- colnames(final.predictors_try2[,13:23])[apply(data.frame(matrix(unlist(final.predictors_try2[,13:23]), nrow=nrow(final.predictors_try2[,13:23]), byrow=T),stringsAsFactors=FALSE), 1, which.max)]

#Relace p with EndGr
BelongsTo_endGrp <- gsub("p","EndGr",BelongsTo_endGrp)

final.predictors_try3 <- cbind(final.predictors_try2, BelongsTo_endGrp)
#Which group is this maximum value

```
# NEXT *******************

#4 Prediction: WE1.5 Algorithms for prediction of expected values of any index based on probability of end group 
# membership and average values of the index amongst reference sites in each end group. Algorithms for taxonomic 
# prediction (including prediction of occurrence and expected abundances
#Start with END_GROUP_INDEX prediction

```{r}
#Calculations for TL2 WHPT NTAXA, ASPT for spring and autumn

# Read the Excel file with endGroup means for another excel input ***
#filepathname <- paste0(path,"/datafiles/x103 End Group Means (FORMATTED).csv")
filepathname <- paste0(path_datafiles,"/x103EndGroupMeans(FORMATTED)(v.JDB17Dec2019).csv") # x103EndGroupMeans(FORMATTED).csv")
# 
endgroup_IndexFrame <- getEndGroupMeans_dtableCopy (filepathname, model)
# Sort by the columns "EndGrp", "SeasonCode"
endgroup_IndexFrame <- arrange(endgroup_IndexFrame, EndGrp, SeasonCode)

# Prepare what you want to run - seasons, indices, and subset the data with the seasonCodes
endgroup_IndexFrame <- filter(endgroup_IndexFrame, SeasonCode %in% SEASONS_TO_RUN)

#Write a function that extracts user input columns and coverts them to the values in c("") below :: USER INPUT
# Run the index Scores   
indices_to_run <- names(endgroup_IndexFrame)[-1:-3] #

mainData <- getSeasonIndexScores_new (final.predictors_try3, SEASONS_TO_RUN, indices_to_run, endgroup_IndexFrame, model)# Change in AZURE

# Remove failing sites from biologicalData: 
# BUG, changed to anti-join. Watch in AZURE the anti-join
          # OLD # biologicalData <- biologicalData[!(biologicalData$SITE %in% this_failing$SITE),]
biologicalData <-  anti_join(biologicalData, this_failing)

#remove column site 
biologicalData <- biologicalData[,-1]
#Bind the biologicalData to all the processed data
#mainData <- cbind(mainData, biologicalData)

resultsFolder <- ("C:/DEFRA/Phase2/AllIndices/NI-Results/")
writeToFile (mainData, resultsFolder, "FinalPredictions_NI_data.csv") 

```
  